### 2019-04-17 report/chapter03.Rnw
Function update

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8, fig.height=3.5,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

require(biostatUZH)
require(tidyverse)
require(meta)
require(xtable)
@

@@

@@

@@

<<echo=FALSE, warning=FALSE>>=
n.bin <- dim(meta.bin)[1]
rejection.bin <- meta.bin %>% summarize(egger.rejection = mean(egger.test),
                                            schwarzer.rejection = mean(schwarzer.test),
                                            rucker.rejection = mean(rucker.test),
                                            harbord.rejection = mean(harbord.test),
                                            peter.rejection = mean(peter.test))

bin.spread <- meta.bin %>% select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% gather(key = test.type, value = "null.hypothesis")
bin.spread$null.hypothesis <- ifelse(bin.spread$null.hypothesis == 1, "rejected", "not rejected")
bin.spread$null.hypothesis <- factor(bin.spread$null.hypothesis)

meta.bin <- meta.bin %>% mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                         egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
                                         egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
                                         egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
                                         schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
                                         schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
                                         schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
                                         rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
                                         rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
                                         harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))

agreement.bin <- meta.bin %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                        egger.peter = sum(egger.peter == "agree")/n(),
                                        egger.rucker = sum(egger.rucker == "agree")/n(),
                                        egger.harbord = sum(egger.harbord == "agree")/n(),
                                        schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
                                        schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
                                        schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
                                        rucker.peter = sum(rucker.peter == "agree")/n(),
                                        harbord.peter = sum(harbord.peter == "agree")/n())

correlation.bin <- meta.bin %>% summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                            egger.peter = cor(pval.egger.bin, pval.peter.bin),
                                            egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
                                            egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
                                            schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
                                            schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
                                            schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
                                            rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
                                            harbord.peter = cor(pval.harbord.bin, pval.peter.bin))

@@

#Continuous outcomes:
n.cont <- dim(meta.cont)[1]
rejection.cont <- meta.cont %>% summarize(egger.rejection = mean(egger.test),
                                              begg.rejection = mean(begg.test),
                                              thomson.rejection = mean(thomson.test))

cont.spread <- meta.cont %>% select(egger.test, begg.test, thomson.test) %>% gather(key = test.type, value = "null.hypothesis")
cont.spread$null.hypothesis <- ifelse(cont.spread$null.hypothesis == 1, "rejected", "not rejected")
cont.spread$null.hypothesis <- factor(cont.spread$null.hypothesis)

meta.cont <- meta.cont %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))

agreement.cont <- meta.cont %>% summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                              thomson.begg = sum(thomson.begg == "agree")/n(),
                                              egger.begg = sum(egger.begg == "agree")/n())

correlation.cont <- meta.cont %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))

@@

@@

trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)
@

@@

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes. From \Sexpr{n.cont} meta-analyses with continouos outcomes, most meta-analyses with rejected null hypotheses have been found by the Thompson and Sharp test (\Sexpr{round(rejection.cont$thomson.rejection, 3)}), followed closely by Eggers test (\Sexpr{round(rejection.cont$egger.rejection, 3)}) and Begg and Mazumdar's test (\Sexpr{round(rejection.cont$begg.rejection, 3)}).
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}). The test that rejects most null hypotheses is here Egger's test (\Sexpr{round(rejection.bin$egger.rejection, 3)}), followed by R\"ucker's test (\Sexpr{round(rejection.bin$rucker.rejection, 3)}), Harbord's test (\Sexpr{round(rejection.bin$harbord.rejection, 3)}), Peters test (\Sexpr{round(rejection.bin$peter.rejection, 3)}) and Schwarzer's test (\Sexpr{round(rejection.bin$schwarzer.rejection, 3)}).

\begin{figure}
<<echo=FALSE>>=
cont.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis )) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=

bin.spread %>% ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + theme_bw()
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

@@

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of two tests are shown with respect to the sample size of the studies in Figure \ref{pvalues.samplesize.bin} for peters test based on dichotomous outcomes and in Figure \ref{pvalues.samplesize.cont} for thomson and sharp's test based on continuous outcomes. %(Suggests that 10 is likely too small)
A trend towards more significant p-values is visible for larger sample sizes.

\begin{figure}
<<echo=FALSE>>=
meta.bin %>% filter(n < 100)%>% ggplot(aes(y = pval.peter.bin, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of peters test for small study effects and their corresponding sample size (dichotomous outcomes)}
\label{pvalues.samplesize.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
meta.cont %>% filter(n < 100) %>% ggplot(aes(y = pval.thomson.cont, x = n)) + geom_point(alpha = 0.5) + theme_bw() + geom_smooth(method = "loess", se = F) 
@
\caption{P-values of thomson and sharp's test for small study effects and their corresponding sample size (continuous outcomes)}
\label{pvalues.samplesize.cont}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}. A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

\begin{figure}
<<echo=FALSE>>=
meta.cont %>% ggplot(aes(x = missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with continuous outcomes.}
\label{trimfill.cont}
\end{figure}

The mean fraction of trimmed comparisons for continuous outcomes is \Sexpr{round(trimfill.cont.mean,2)} and the median \Sexpr{round(trimfill.cont.median,2)}.

The same is repeated for binary outcomes in figure \ref{trimfill.bin}. 
\begin{figure}
<<echo=FALSE>>=
meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
  theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
@
\caption{Histogram of fractions of trimmed comparisons from meta analyses with binary outcomes.}
\label{trimfill.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = meta.bin$missing.trim.bin, y = as.factor(ifelse(meta.bin$peter.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
\label{trimfill.pvalues.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
cdplot(x = meta.cont$missing.trim.cont, y = as.factor(ifelse(meta.cont$thomson.test == 1, "yes", "no")), xlab = "Fraction of added studies", ylab = "Bias")
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
\label{trimfill.pvalues.cont}
\end{figure}

\subsection{Small Study Effect Correction}

Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.

>>>>

<<echo=FALSE>>=
library(knitr)
opts_chunk$set(fig.path='figure/ch02_fig',
               echo=TRUE, message=FALSE,
               fig.width=8.1, fig.height=3.5,
               out.width='\\textwidth-3cm',
               message=FALSE, fig.align='center',
               background="gray98", tidy=FALSE, #tidy.opts=list(width.cutoff=60),
               cache=TRUE
)
options(width=74)
@

@@

require(biostatUZH)
require(tidyverse)
require(gridExtra)
require(meta)
require(xtable)
@

@@

<<echo=FALSE>>=
meta <- bind_rows(meta.bin, meta.cont)
meta <- meta %>% mutate(sig.ranef = ifelse(!is.na(sig.ranef.bin), sig.ranef.bin, sig.ranef.cont),
                        thomson.test = ifelse(!is.na(thomson.test), thomson.test, rucker.test),
                        sig.fixef = ifelse(!is.na(sig.fixef.bin), sig.fixef.bin, sig.fixef.cont),
                        sig.reg.random = ifelse(!is.na(sig.reg.random.bin), sig.reg.random.bin, sig.reg.random.cont),
                        missing.trim = ifelse(!is.na(missing.trim.bin), missing.trim.bin, missing.trim.cont),
                        pval.thomson = ifelse(!is.na(pval.rucker.bin), pval.rucker.bin, pval.thomson.cont))
@

@@

It is also possible to look how the amount of meta-analysis with significant pooled effect size estimates changes over time, e.g. mean publication year (of studies included in the meta-analysis). 0.05 is used here as the threshold for $p$-value significance and subsequent null-hypothesis rejection. To constrict random fluctuation in the proportion, only mean publication years with a certain amount of meta-analyses are shown ($n < 180$). The $p$-value of the fixed effects meta analysis model is used to decide about rejection of the null-hypothesis. As Figure \ref{treatment.effect.significance.overtime} shows, the proportion of meta-analyses with significant treatment effect estimates stays roughly constant over time.

\begin{figure}
<<echo=FALSE>>=
meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
  ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef), stat(count))) + geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
@
\caption{Proportion of significant treatment effect estimates over time (mean publication year).}
\label{effect.samplesize}
\end{figure}

A somewhat different question is how statistical power of studies changed over time. As an approximation, the total sample size of a study can be used. Figure \ref{median.samplesize.overtime} shows the median sample size of all studies of a given year. Again, to reduce the effects of distortion due to random fluctuation, only the medians for the years 1980 to 2017 are used ($n$ > 50,000).

\begin{figure}
<<echo=FALSE>>=
data %>% distinct(study.name, .keep_all = T) %>%  filter(study.year < 2018 & study.year > 1980) %>% group_by(study.year) %>% 
  summarize(samplesize = median(total1 + total2, na.rm = T)) %>% 
  ggplot(aes(y = samplesize, x = study.year)) + geom_line()
@
\caption{Median sample size over time (years).}
\label{median.samplesize.overtime}
\end{figure}

@@

<<echo=FALSE, warning=FALSE>>=
#Test Results: Binary
test.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                          schwarzer.test = mean(schwarzer.test),
                                                          rucker.test = mean(rucker.test),
                                                          harbord.test = mean(harbord.test),
                                                          peter.test = mean(peter.test))
test.bin <- test.bin %>% gather(key = "test.type", value = "mean")

p.bin <- meta.bin %>% filter(sig.fixef.bin == 1) %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>%  
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) +
  annotate("text", x = test.bin$test.type, y = 1000, 
           label = paste(round(test.bin$mean, 2)*100, "% rejected"), 
           color = "white")

test.sig.bin <- meta.bin %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                              schwarzer.test = mean(schwarzer.test),
                                                              rucker.test = mean(rucker.test),
                                                              harbord.test = mean(harbord.test),
                                                              peter.test = mean(peter.test))
test.sig.bin <- test.sig.bin %>% gather(key = "test.type", value = "mean")

p1 <- meta.bin %>% ungroup() %>% 
select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
  annotate("text", x = test.sig.bin$test.type, y = 1750, 
           label = paste(round(test.sig.bin$mean, 2)*100, "% rejected"), 
           color = "white")

test.nonsig.bin <- meta.bin %>% filter(sig.fixef.bin == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                                                                schwarzer.test = mean(schwarzer.test),
                                                                                                rucker.test = mean(rucker.test),
                                                                                                harbord.test = mean(harbord.test),
                                                                                                peter.test = mean(peter.test))
test.nonsig.bin <- test.nonsig.bin %>% gather(key = "test.type", value = "mean")

p2 <- meta.bin %>% 
  filter(sig.fixef.bin == 0) %>% ungroup() %>% 
  select(egger.test, schwarzer.test, rucker.test, harbord.test, peter.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) +theme(legend.position="none") +
  annotate("text", x = test.nonsig.bin$test.type, y = 650, 
           label = paste(round(test.nonsig.bin$mean, 2)*100, "% rejected"), 
           color = "white")

#Test Results: Continuous
test.cont <- meta.cont %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                            begg.test = mean(begg.test),
                                                            thomson.test = mean(thomson.test))

test.cont <- test.cont %>% gather(key = "test.type", value = "mean")

p.cont <- meta.cont %>% ungroup() %>% 
  select(egger.test, thomson.test, begg.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + xlab(label = NULL) +
  annotate("text", x = test.cont$test.type, y = 750, 
           label = paste(round(test.cont$mean, 2)*100, "% rejected"), 
           color = "white")

test.sig.cont <- meta.cont %>% filter(sig.fixef.cont == 1) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                                                                begg.test = mean(begg.test),
                                                                                                thomson.test = mean(thomson.test))

test.sig.cont <- test.sig.cont %>% gather(key = "test.type", value = "mean")

p3 <- meta.cont %>% 
  filter(sig.fixef.cont == 1) %>% ungroup() %>% 
  select(egger.test, thomson.test, begg.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
  annotate("text", x = test.sig.cont$test.type, y = 600, 
           label = paste(round(test.sig.cont$mean, 2)*100, "% rejected"), 
           color = "white")

test.nonsig.cont <- meta.cont %>% filter(sig.fixef.cont == 0) %>% ungroup() %>% summarize(egger.test = mean(egger.test),
                                                                                                   begg.test = mean(begg.test),
                                                                                                   thomson.test = mean(thomson.test))

test.nonsig.cont <- test.nonsig.cont %>% gather(key = "test.type", value = "mean")

p4 <- meta.cont %>% 
  filter(sig.fixef.cont == 0) %>% ungroup() %>% 
  select(egger.test, thomson.test, begg.test) %>% 
  gather(key = "test.type", value = "null.hypothesis") %>% 
  mutate(null.hypothesis = factor(ifelse(null.hypothesis == 1, "rejected", "not rejected"))) %>% 
  ggplot(aes(x = test.type, fill = null.hypothesis)) + geom_bar() + coord_flip() + 
  theme_bw() + ggtitle("Non-significant Pooled Effects")+ xlab(label = NULL) + theme(legend.position="none") +
  annotate("text", x = test.nonsig.cont$test.type, y = 100, 
           label = paste(round(test.nonsig.cont$mean, 2)*100, "% rejected"), 
           color = "white")

########################################################################################################################################
########################################################################################################################################

#Agreement proportions of publication bias tests:

#Binary:
n.bin <- dim(meta.bin)[1]
meta.bin <- meta.bin %>%ungroup() %>%  mutate(egger.schwarzer = ifelse(egger.test == schwarzer.test, "agree", "disagree"),
                                        egger.peter = ifelse(egger.test == peter.test, "agree", "disagree"),
                                        egger.rucker = ifelse(egger.test == rucker.test, "agree", "disagree"),
                                        egger.harbord = ifelse(egger.test == harbord.test, "agree", "disagree"),
                                        schwarzer.peter = ifelse(schwarzer.test == peter.test, "agree", "disagree"),
                                        schwarzer.rucker = ifelse(schwarzer.test == rucker.test, "agree", "disagree"),
                                        schwarzer.harbord = ifelse(schwarzer.test == harbord.test, "agree", "disagree"),
                                        rucker.peter = ifelse(rucker.test == peter.test, "agree", "disagree"),
                                        rucker.harbord = ifelse(rucker.test == harbord.test, "agree", "disagree"),
                                        harbord.peter = ifelse(harbord.test == peter.test, "agree", "disagree"))

agreement.bin <- meta.bin %>% ungroup() %>% summarise(egger.schwarzer = sum(egger.schwarzer == "agree")/n(),
                                            egger.peter = sum(egger.peter == "agree")/n(),
                                            egger.rucker = sum(egger.rucker == "agree")/n(),
                                            egger.harbord = sum(egger.harbord == "agree")/n(),
                                            schwarzer.peter = sum(schwarzer.peter == "agree")/n(),
                                            schwarzer.rucker = sum(schwarzer.rucker == "agree")/n(),
                                            schwarzer.harbord = sum(schwarzer.harbord == "agree")/n(),
                                            rucker.peter = sum(rucker.peter == "agree")/n(),
                                            harbord.peter = sum(harbord.peter == "agree")/n())

correlation.bin <- meta.bin %>%ungroup() %>%  summarise(egger.schwarzer = cor(pval.egger.bin, pval.schwarzer.bin),
                                              egger.peter = cor(pval.egger.bin, pval.peter.bin),
                                              egger.rucker = cor(pval.egger.bin, pval.rucker.bin),
                                              egger.harbord = cor(pval.egger.bin, pval.harbord.bin),
                                              schwarzer.peter = cor(pval.schwarzer.bin, pval.peter.bin),
                                              schwarzer.rucker = cor(pval.schwarzer.bin, pval.rucker.bin),
                                              schwarzer.harbord = cor(pval.schwarzer.bin, pval.harbord.bin),
                                              rucker.peter = cor(pval.rucker.bin, pval.peter.bin),
                                              harbord.peter = cor(pval.harbord.bin, pval.peter.bin))

@@

#Continuous:
n.cont <- dim(meta.cont)[1]
meta.cont <- meta.cont %>% ungroup() %>% mutate(thomson.egger = ifelse(thomson.test == egger.test, "agree", "disagree"),
                                          thomson.begg = ifelse(thomson.test == begg.test, "agree", "disagree"),
                                          egger.begg = ifelse(egger.test == begg.test, "agree", "disagree"))

agreement.cont <- meta.cont %>% ungroup() %>%  summarise(thomson.egger = sum(thomson.egger == "agree")/n(),
                                              thomson.begg = sum(thomson.begg == "agree")/n(),
                                              egger.begg = sum(egger.begg == "agree")/n())

correlation.cont <- meta.cont %>% ungroup() %>% summarise(thomson.egger = cor(pval.thomson.cont, pval.egger.cont),
                                                thomson.begg = cor(pval.thomson.cont, pval.begg.cont),
                                                egger.begg = cor(pval.egger.cont, pval.begg.cont))

@@

########################################################################################################################################
########################################################################################################################################

@@

trimfill.bin.mean <- meta.bin %>% ungroup %>% summarise(mean = mean(missing.trim.bin)) %>% select(mean)
trimfill.bin.median <- meta.bin %>% ungroup %>% summarise(median = median(missing.trim.bin)) %>% select(median)

# meta.bin %>% ggplot(aes(x = missing.trim.bin)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (binary outcome)") + xlab("Fraction") + ylab("Frequency")
# 
# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont)) + geom_histogram(col = "gray15", fill = "dodgerblue") +
#   theme_bw() + labs(title = "Fraction of Trimmed Comparisons (continuous outcome)") + xlab("Fraction") + ylab("Frequency")
# 
# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
# 
# meta.bin %>% ggplot(aes(x = missing.trim.bin, fill = factor(harbord.test))) + geom_density(na.rm = T, position = "fill")
# 
# meta.cont %>% ggplot(aes(x = missing.missing.trim.cont, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
# 
# #Time trends in significance of tests
# meta.bin %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_histogram()
# 
# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
# 
# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.bin))) + geom_density(na.rm = T, position = "fill")
# 
# meta.bin %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
#   ggplot(aes(x = first.publication.year, fill = factor(peter.test))) + geom_density(na.rm = T, position = "fill")
# 
# meta.bin %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(rucker.test))) + geom_density(na.rm = T, position = "fill")
# 
# 
# meta.cont %>% filter(mean.publication.year < 2019 & mean.publication.year > 1960) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_histogram()
# 
# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
# 
# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
#   ggplot(aes(x = first.publication.year, fill = factor(sig.fixef.cont))) + geom_density(na.rm = T, position = "fill")
# 
# meta.cont %>% filter(first.publication.year < 2013 & first.publication.year > 1990) %>% 
#   ggplot(aes(x = first.publication.year, fill = factor(thomson.test))) + geom_density(na.rm = T, position = "fill")
# 
# meta.cont %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
#   ggplot(aes(x = mean.publication.year, fill = factor(egger.test))) + geom_density(na.rm = T, position = "fill")
# 
# 
# data %>% filter(study.year < 2019 & study.year > 1980) %>% group_by(study.year) %>% summarize(samplesize = mean(total1 + total2, na.rm = T)) %>% 
#   ggplot(aes(y = samplesize, x = study.year)) + geom_line()

@

@@

\vspace{0mm}
There are modifications to make tests more appropriate in case of binary outcomes, therefore the results have been separated in continuous and dichotomous outcome test results. In Figure \ref{bias.results.cont} the proportion of test results that led to rejection of the null hypothesis of no small study effect based on the 5 \% level are shown for continuous outcomes ($n$ = \Sexpr{n.cont})
The same is shown in Figure \ref{bias.results.bin} for dichotomous outcome measures ($n$ = \Sexpr{n.bin}).

\begin{figure}
<<echo=FALSE>>=
plot(p.cont)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
plot(p.bin)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin}
\end{figure}

The same plots can be shown separately for meta-analyses with significant and non-significant pooled effect sizes. This is done in Figure \ref{bias.results.cont.sep} for continuous outcomes and \ref{bias.results.bin.sep} for binary outcomes.

\begin{figure}
<<echo=FALSE>>=
grid.arrange(p3, p4, ncol = 2)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (continuous outcomes).}
\label{bias.results.cont.sep}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
grid.arrange(p1, p2, ncol = 2)
@
\caption{Proportion where the null hypothesis of no small study effect is rejected based on the 5\% significance level for different tests (dichotomous outcomes).}
\label{bias.results.bin.sep}
\end{figure}

Furthermore one can look if the frequencies of tests that reject the null hypotheses change over time (mean publication year of the studies included in the meta analyses). The proportion of the test results are shown in Figure \ref{pub.bias.time.overtime}. The Figure suggests that the frequency of publication bias remains constant over time. The mean publication years have been restricted such that at least 180 meta-analyses are available per year such that random fluctuation is restricted to some extent. The significance threshold for the $p$-values used is 0.05, and the small study effect test used is Thomson's test (with the arcsine variance stabilizing transformation function used in the case of binary outcomes).

\begin{figure}
<<echo=FALSE>>=
meta %>% filter(mean.publication.year < 2013 & mean.publication.year > 1990) %>% 
  ggplot(aes(x = mean.publication.year, fill = factor(thomson.test), stat(count))) + geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
@
\caption{Proportion of test results where the null hypothesis of no small study effect is rejected over time (mean publication.year).}
\label{pub.bias.overtime}
\end{figure}

@@

\vspace{0mm}
Test performance depends on the sample size, despite having restricted sample size to a minimum of 10 studies. The p-values of the Thompson and Sharp tests are shown with respect to the sample size of the meta-analysis in Figure \ref{pvalues.samplesize}. %(Suggests that 10 is likely too small)
In the case of binary outcomes, the arcsine variance stabilizing function has been applied prior to use of Thompson and Sharp's test. A s trend towards more rejections for larger sample sizes can be seen.

\begin{figure}
<<echo=FALSE>>=
meta %>% filter(n < 40) %>% ggplot(aes(stat(count), x = n, fill = factor(thomson.test))) + 
  geom_density(position = "fill")
@
\caption{P-values of Thomson and Sharp's test for small study effects and their corresponding sample size.}
\label{pvalues.samplesize}
\end{figure}

\vspace{0mm}
One can use the proportion of added studies by the trim-and-fill method from the overall number of studies to further investigate the extent of small study effects. The mean fraction of trimmed comparisons for binary outcomes is \Sexpr{round(trimfill.bin.mean,2)} and the median \Sexpr{round(trimfill.bin.median,2)}. 
% A histogram with those fractions is shown in Figure \ref{trimfill.cont} for continuous outcomes and \ref{trimfill.bin} for dichotomous outcomes. In both cases, the method very commonly adds supposedly unpublished studies to the meta-analyses. 
In Figure \ref{trimfill.pvalues.bin} and Figure \ref{trimfill.pvalues.cont}, the relationship between fraction of added studies by trim-and-fill and the hypothesis test decisions of the small study effects tests is shown for continuous and dichotomous outcomes. In the case of Peters test dor dichotomous outcomes, there is less agreement with the trim-and fill method than in the case of Thomson and Sharp's test for continuos outcomes in the sense that the fraction of meta-analyses with rejected null hypothesises increases more clearly when there are more studies added by trim-and-fill.

\begin{figure}
<<echo=FALSE>>=
meta.bin %>% filter(missing.trim.bin < 0.5) %>% 
  ggplot(aes(x = missing.trim.bin, fill = factor(peter.test), stat(count))) + 
  geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Peters test and dichotomous outcomes}
\label{trimfill.pvalues.bin}
\end{figure}

\begin{figure}
<<echo=FALSE>>=
meta.cont %>% filter(missing.trim.cont < 0.5) %>% 
  ggplot(aes(x = missing.trim.cont, fill = factor(thomson.test), stat(count))) + 
  geom_density(na.rm = T, position = "fill") + 
  labs(fill = "Significance") + scale_fill_discrete(labels= c("Yes", "No"))
@
\caption{Fraction of added studies for small study effect correction by trim and fill and the corresponding small study effect test decision (based on 5\% significance level) of Thomson and Sharp's test and continuous outcomes}
\label{trimfill.pvalues.cont}
\end{figure}

\subsection{Small Study Effect Correction}
Multiple methods are available to correct for the effects of small study effects in order to get an unbiased estimate.
